\PaperTitle

### 2020-01-26 paper/filter_bubbles.tex
updates

% Anonymized submission.
\author{Submission 42?}

% Abstract. Note that this must come before \maketitle.
\begin{abstract}
We study a model of user decision-making in the context of recommender systems. We explore the extent to which two issues traditionally associated with recommender systems -- \textit{filter bubbles} and \textit{user homogenization} -- can be attributed to recommendation systems. In our model users face a sequential decision problem under uncertainty and there are informational spillovers where a user consuming a product and learning how she values it reduces uncertainty and provides information about similar products. We find that this generates behavior consistent with filter bubble effects -- where users consume increasingly similar items over time -- and that recommendation can help alleviate these effects, as has been found in the empirical work of Nguyen et al. (2014). However, we find that recommendation, while alleviating filter bubble effects, leads to an increase in user homogeneity. Our results highlight the path-dependence of user choice in environments where recommender systems are deployed.
\end{abstract}

@@

Suppose instead that item 0 ends up having a negative valuation so that $y = -0.5 < 0$. Now we have that $\mathbb{E}[x_1] = \mathbb{E}[x_3] = -\frac{1}{4} <  -\frac{1}{8} = \mathbb{E}[x_2]$ with $\bar{\Sigma}$ remaining the same as when $y = 0.5$. Now, the risk-aversion levels of the user determine the choice in the next period. If the user is risk-neutral ($\gamma = 0$), then she will go across the product space to consume item $2$ in the next period since it has a higher expected value. However, if she is sufficiently risk-averse then she still may consume item $1$ or $3$ since her uncertainty about these items is lower than item $2$. In particular, this will happen when 

>>>>

% Anonymized submission.
\author{Submission 20}

% Abstract. Note that this must come before \maketitle.
\begin{abstract}
We study a model of user decision-making in the context of recommender systems via numerical simulation. We explore the extent to which two issues traditionally associated with recommender systems -- \textit{filter bubbles} and \textit{user homogenization} -- can be attributed to recommendation systems. In our model users face a sequential decision problem under uncertainty and there are informational spillovers where a user consuming a product and learning how she values it reduces uncertainty and provides information about similar products. We find that this generates behavior consistent with filter bubble effects -- where users consume increasingly similar items over time -- and that recommendation can help alleviate these effects, as has been found in the empirical work of Nguyen et al. (2014). However, we find that recommendation, while alleviating filter bubble effects, leads to an increase in user homogeneity. Our results highlight the path-dependence of user choice in environments where recommender systems are deployed.
\end{abstract}

@@

Suppose instead that item 0 ends up having a negative valuation so that $y = -0.5 < 0$. This results in $\mathbb{E}[x_1] = \mathbb{E}[x_3] = -\frac{1}{4} <  -\frac{1}{8} = \mathbb{E}[x_2]$ with $\bar{\Sigma}$ remaining the same as when $y = 0.5$. In this case the risk-aversion levels of the user determine the choice in the next period. If the user is risk-neutral ($\gamma = 0$), then she will go across the product space to consume item $2$ in the next period since it has a higher expected value. However, if she is sufficiently risk-averse then she still may consume item $1$ or $3$ since her uncertainty about these items is lower than item $2$. In particular, this will happen when 
